CE888 Assignment 1

### 2019-02-19 paper/main.tex
update

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{A}{uto} encoders are 
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\subsection{Subsection Heading Here}
Subsection text here.

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

>>>>

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{U}{nsupervised} learning is a branch of machine learning that deals with unlabeled data to find patterns, groups
and relations. This sub section of machine learning is useful to describe and understand unknown data, which 
also helps us understand the properties of future data samples. Right now we are collecting data much faster than we can process it.
And most of the time the data we acquire is unlabeled, and these huge amounts of data are complex, noisy
and it might include unnecessary information.\par There are different ways to reduce the complexity of a given data and learn good 
features from it. In this work, we will look at auto encoders, one of those procedures used to learn features from a given data.
Auto encoders are a part of representational learning, which can be trained with or without labels.
They play a key role in deep learning applications. They are used in dimensionality reduction and feature 
extraction, and together with deep learning they gained a lot of traction after Hinton proposed a method to train 
deep belief networks one layer at a time [2]. The motivation for using auto encoders is, in what they do they are
very similar to traditional feature selection algorithms, but they are also capable of learning good features from
complex and high dimensional data. This aspect of auto encoders and unsupervised learning in general is important.
As LeCun states in [3], people are not paying attention to unsupervised learning because of the success of the supervised learning
in recent years. But it will be far more important in the future because of how living beings perceive and learn, they do not
need labels to recognize the world around them.\par In this paper we are going to look at previous work (Section II),
look at different methods and present their results to show how they compare. In Section III, we are going to present 
our goals and what we want to accomplish. Then we will talk about the datasets that we are going to use for the task and 
give detailed information about them. The planned experiments and analyses for the task will be mentioned in Section IV.
Evaluation methods that are going to be used after the experiments will be presented in Section V.

\section{Background}
The conclusion goes here.
% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}
